Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-15 paper.tex
Correct and add details to AoU text

\subsection{Case study: All of Us exome-like data} 
The All of Us dataset comprises 245,388 clinical-grade whole genome sequences,
identifying over 1 billion variants, including 3.9 million novel variants with
coding consequences~\citep{all2024genomic}. 
Participants are from the United States, with an emphasis
on historically underrepresented genetic ancestry groups. The genomic data is
of high quality, with an average coverage depth of 30x, and is linked to
extensive health-related information, providing a valuable resource for
biomedical research. For this study, we applied the bio2zarr compression method
to the exome-like data for chromosome 20 from All of Us. This dataset, stored as a
compressed VCF file of 7.44 GiB, includes 681,000 variants, of which 746 are
classified as pathogenic or likely pathogenic.

>>>>

\subsection{Case study: All of Us exome-like data} 
The All of Us dataset comprises 245,388 clinical-grade whole genome sequences (WGS), 
identifying over 1 billion variants, including 3.9 million novel variants 
with coding consequences~\citep{all2024genomic}. Participants are from the United States, 
with an emphasis on historically underrepresented genetic ancestry groups. 
The genomic data, generated through short-read sequencing on the Illumina NovaSeq 6000, 
is of high quality, with an average coverage depth of 30x, and is linked to extensive 
health-related information, providing a valuable resource for biomedical research. 
WGS analysis is conducted on the Illumina DRAGEN platform, with alignment performed 
using the GRCh38dh reference genome. GTC files are converted to VCF format using 
Picard GtcToVcf, and every step of the WGS procedure is rigorously controlled by 
predefined quality control measures.

For this study, we applied the bio2zarr compression to the chromosome 20 exome-like 
data from the All of Us dataset. The exome-like data is constructed by extracting from the WGS 
the SNP and Indel variants that lie within the chromosome 20 exon regions of the Gencode v42 basic 
transcripts for all samples. This dataset, stored as a compressed VCF file of 7.44 GiB, 
includes 715,256 variants, of which 746 are classified as pathogenic or likely pathogenic.
